fatigue

### 2023-10-30 inst/fatigue.Rmd
label all chunks

```{r cars}
jj <- read.table("interzonal1973_petropolis.txt",header=TRUE,skip=2)
a <- data.frame(day=jj$day + 31*(jj$month=="August"),white=jj$white,black=jj$black,result=jj$result,round=jj$round,moves=jj$moves)

@@

```{r}
tab <- cbind(tab,played=rowSums(tab))
tab <- cbind(tab,points=tab[,1] + tab[,3]/2)
tab
```

```{r}
table(a$result)
hist(a$moves)
plot(moves~as.factor(result),data=a)
result
moves_drawn_games <- a$moves[a$result == "1/2-1/2"]
moves_won_games   <- a$moves[a$result != "1/2-1/2"]
t.test(moves_drawn_games,moves_won_games)
```

```{r}
head(a,10)
o <- matrix(0,max(a[,5]),length(players))
dimnames(o) <- list(round=paste("r",seq_len(nrow(o)),sep=""),player=players)

@@

```{r}
unlist(a[2,])
`fatigued` <- function(i){
  x <- unlist(a[i,])
  day <- as.numeric(a[i,1])
  white_player <- a[i,2]
  black_player <- a[i,3]
  result <- a[i,4]
  round <- as.numeric(a[i,5])
  out <- c(white_player_fatigued=FALSE,black_player_fatigued=FALSE)

@@

```{r}
summary(Hf)
pnames(Hf)
Hf_maxp
pie(Hf_maxp)
```

```{r}
jj <- rep(0,nrow(a))
M <- data.frame(
white_player=rep(NA,nrow(a)),
black_player=rep(NA,nrow(a)),
white_player_fatigued=FALSE,
black_player_fatigued=FALSE
)
for(i in seq_len(nrow(a))){
	M[i,1] <- a[i,2]	
	M[i,2] <- a[i,3]	
	jj <- fatigued(i)
	M[i,3] <- jj[1]
	M[i,4] <- jj[2]
}
colnames(M) <- c("white","black","white_fatigued","black_fatigued")
tail(M)
table(M[,3])
table(M[,4])
```

>>>>

```{r readdata}
jj <- read.table("interzonal1973_petropolis.txt",header=TRUE,skip=2)
a <- data.frame(day=jj$day + 31*(jj$month=="August"),white=jj$white,black=jj$black,result=jj$result,round=jj$round,moves=jj$moves)

@@

```{r maketabs}
tab <- cbind(tab,played=rowSums(tab))
tab <- cbind(tab,points=tab[,1] + tab[,3]/2)
tab
```

```{r dostudentttest}
table(a$result)
hist(a$moves)
plot(moves~as.factor(result),data=a)
result
moves_drawn_games <- a$moves[a$result == "1/2-1/2"]
moves_won_games   <- a$moves[a$result != "1/2-1/2"]
t.test(moves_drawn_games,moves_won_games)
```

```{r makeo}
head(a,10)
o <- matrix(0,max(a[,5]),length(players))
dimnames(o) <- list(round=paste("r",seq_len(nrow(o)),sep=""),player=players)

@@

```{r justsuccessive}
unlist(a[2,])
`fatigued` <- function(i){
  x <- unlist(a[i,])
  day <- as.numeric(a[i,1])
  white_player <- a[i,2]
  black_player <- a[i,3]
  result <- a[i,4]
  round <- as.numeric(a[i,5])
  out <- c(white_player_fatigued=FALSE,black_player_fatigued=FALSE)

@@

```{r showsum}
summary(Hf)
pnames(Hf)
Hf_maxp
pie(Hf_maxp)
```

```{r maketable}
jj <- rep(0,nrow(a))
M <- data.frame(
white_player=rep(NA,nrow(a)),
black_player=rep(NA,nrow(a)),
white_player_fatigued=FALSE,
black_player_fatigued=FALSE
)
for(i in seq_len(nrow(a))){
	M[i,1] <- a[i,2]	
	M[i,2] <- a[i,3]	
	jj <- fatigued(i)
	M[i,3] <- jj[1]
	M[i,4] <- jj[2]
}
colnames(M) <- c("white","black","white_fatigued","black_fatigued")
tail(M)
table(M[,3])
table(M[,4])
```
